### 2015-11-05 CVPR16/Source/applications.tex
Moving some content from experiments.tex to application.tex and experiments2.tex

\subsection{3D Object Localization}
To show the effectiveness of our method we apply it to the localization
problem. We estimate the position, orientation and dimensions of the car with
our framework and compute the error in birds eye view domain along the ground
plane. We report error in three metrics translation error (t) in meters per
car, yaw error (yaw) in radians per car and dimension error is again meters per
car. The results are shown in Table~\ref{tab:localizationExperiment}.

We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
allows us to factorize the intractable probability distribution into following form
%
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  -Z' 
  \\
  + \sum_{t=s_i}^{e_i}
  \left(
  \sum_{i,j:i\ne j}   
  \WEnergyCol 
   + \WpEnergy{bbox}
   + \WpEnergy{track}
\right)
  \\
  + \left(
  \sum_{i=1}^N 
  \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace.
\end{multline}
%
Next, we explain the important energies used in our graphical model.

@@

\subsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution.

>>>>

\subsection{3D Object Localization}
To show the effectiveness of our method we apply it to the localization
problem. We estimate the position, orientation and dimensions of the car with
our framework and compute the error in birds eye view domain along the ground
plane. 
To estimate the localization of traffic participants (TPs) in a road scene we follow the graphical model approach.
We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
allows us to factorize the intractable probability distribution into following form
%
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  -Z' 
  \\
  + \sum_{t=s_i}^{e_i}
  \left(
  \sum_{i,j:i\ne j}   
  \WEnergyCol 
   + \WpEnergy{bbox}
   + \WpEnergy{track}
\right)
  \\
  + \left(
  \sum_{i=1}^N 
  \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace.
\end{multline}
%
Next, we explain the important energies used in our graphical model.

@@

\subsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution. We choose Metropolis Hastings inference over
block-coordinate descent which turns out to be slower than Metropolis Hastings
in our experiments. Please refer to our supplementary material for the comparison
of inference methods.

### 2015-11-05 CVPR16/Source/experiments.tex
Moving some content from experiments.tex to application.tex and experiments2.tex

We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
allows us to factorize the intractable probability distribution into following form
%
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  -Z' 
  \\
  + \sum_{t=s_i}^{e_i}
  \left(
  \sum_{i,j:i\ne j}   
  \WEnergyCol 
   + \WpEnergy{bbox}
   + \WpEnergy{track}
\right)
  \\
  + \left(
  \sum_{i=1}^N 
  \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace.
\end{multline}
%
Next, we explain the important energies used in our graphical model.

@@

If we know a portion of our proposed detection bounding box is known to be
occluded, then we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundary of detection bounding boxes, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion we sample
$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
GMM $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{multline}
  S'(\bb{i}) =
  \\
  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{multline}

@@

\subsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution.

>>>>

To estimate the localization of traffic participants (TPs) in a road scene we follow the graphical model approach.
We build the graphical model as shown in Fig~\ref{fig:graphmodel} that 
allows us to factorize the intractable probability distribution into following form
%
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  -Z' 
  \\
  + \sum_{t=s_i}^{e_i}
  \left(
  \sum_{i,j:i\ne j}   
  \WEnergyCol 
   + \WpEnergy{bbox}
   + \WpEnergy{track}
\right)
  \\
  + \left(
  \sum_{i=1}^N 
  \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace.
\end{multline}
%
Next, we explain the formulation of important energies used in our graphical
model.

@@

If we know a portion of our proposed detection bounding box is known to be
occluded, then we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion of interest
is often on the boundary of detection bounding boxes, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion we sample
$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
GMM $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{multline}
  S'(\bb{i}) =
  \\
  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{multline}

@@

\subsection{Metropolis Hastings Inference}
We use Metropolis Hastings' methods for graphical model inference. Since we are
optimizing over continuous random variables, we use Gaussian distribution as
the proposal distribution. We choose Metropolis Hastings inference over
block-coordinate descent which turns out to be slower than Metropolis Hastings
in our experiments. Please refer to our supplementary material for the comparison
of inference methods.

\subsection{Observations}
The results from our localization experiments are shown in Table~\ref{tab:localizationExperiment}. We compare four combinations of energies as shown in the table.
The energy $\EnergyTrackNoOcc$ represents the point tracks energy modeled with 
accounting for occlusion, i.e., we remove the term $\Ptransmission$ and model
$\EnergyTrack$ in the absence of $\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\bSigma$ that accounts for occlusion.
The results show that use of continuous occlusion model 
improves the localization accuracy in terms of all three metrics: translation,
yaw and dimension error.

### 2015-11-05 CVPR16/Source/experiments2.tex
Moving some content from experiments.tex to application.tex and experiments2.tex

>>>>

\subsection{Localization Experiment and Results}
We report error in three metrics translation error (t) in meters per car, yaw
error (yaw) in radians per car and dimension error is again meters per car. The
results are shown in Table~\ref{tab:localizationExperiment}.  We compare four
combinations of energies as shown in the table.  The energy $\EnergyTrackNoOcc$
represents the point tracks energy modeled with accounting for occlusion, i.e.,
we remove the term $\Ptransmission$ and model $\EnergyTrack$ in the absence of
$\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the
modification of $\bSigma$ that accounts for occlusion.  The results show that
use of continuous occlusion model improves the localization accuracy in terms
of all three metrics: translation, yaw and dimension error.
